Cartogram Mapping and its Application to Cancer Data Visualisation

### 2019-08-30 review_article.Rmd
add fig caption to grid image. won't render in pdf

```{r choropleth-grid-create, message=FALSE, fig.cap = "Public facing choropleth cancer maps. [Globocan 2012: Estimated  Cancer Incidence, Mortality and Prevalence](http://globocan.iarc.fr/Pages/Map.aspx), "}
library(grid)
library(png)
library(gridExtra)

@@

```{r choropleth-grid-print, echo = FALSE, results = "asis"}
#knitr::include_graphics("figures/choropleth_grid.png")
```

>>>>

```{r choropleth-grid-create, message=FALSE, fig.caption = "Public facing choropleth cancer maps. From right to left and top to bottom: [1. Globocan 2012: Estimated  Cancer Incidence, Mortality and Prevalence](http://globocan.iarc.fr/Pages/Map.aspx),  [2. Bowel Cancer Australia Atlas](http://www.bowelcanceratlas.org/), [3. Atlas of Cancer in QLD - Lung cancer in males](https://cancerqld.org.au/research/queensland-cancer-statistics/queensland-cancer-atlas/)"}

# fig.cap = "Public facing choropleth cancer maps. From right to left and top to bottom: [1. Globocan 2012: Estimated  Cancer Incidence, Mortality and Prevalence](http://globocan.iarc.fr/Pages/Map.aspx),  [2. Bowel Cancer Australia Atlas](http://www.bowelcanceratlas.org/), [3. Atlas of Cancer in QLD - Lung cancer in males](https://cancerqld.org.au/research/queensland-cancer-statistics/queensland-cancer-atlas/),(http://www.cancer-rates.info/naaccr/), [5. Atlas of Childhood Cancer in Ontario](http://www.pogo.ca/research-data/pogo-atlas/), 6. An Atlas of Cancer in South Australia](https://www.cancersa.org.au/assets/images/pdfs/An%20Atlas%20of%20Cancer%20in%20South%20Australia%20-%20Full%20Report.pdf ), [7. The Environment and Health Atlas of England and Wales](http://www.envhealthatlas.co.uk/eha/Breast/), [8. Map of Cancer Mortality Rates in Spain]() "}

library(grid)
library(png)
library(gridExtra)

@@

```{r choropleth-grid-print, echo = FALSE, results = "asis"}

#knitr::include_graphics("figures/choropleth_grid.png")
```
